Regular singular Volterra equations on complex domains

### 2023-08-15 reg-sing-volterra.tex
Drop old versions of overview of main results proofs

Now we know that $\volterra$ sends $\solproto$ into the affine subspace $\solproto + \singexpalg{\tau-1+\epsilon}(\domain)$, suggesting that the equation $\solwhole = \volterra \solwhole$ has a solution there. To confirm this, we'll show in Section~\ref{sec:V is a contraction} that $\volterra$ is a contraction of $\singexp{\tau-1+\epsilon}{\Lambda}(\domain)$ when $\Lambda$ is large enough. This tells us that $\volterra$ has a unique fixed point in $\solproto + \singexpalg{\tau-1+\epsilon}(\domain)$, as we'll see in Section~\ref{sec:existence and uniqueness}.

%%In Section~\ref{setting}, we built $\volterra$ by taking a separable operator $\hardpart$ with a regular singularity at $\zeta = 0$ and adding a perturbation $\softpart$. Correspondingly, our solution method starts with the prototype solution $\solproto$,

%%In this section, we'll prove the results stated in Section~\ref{sec:results}, which lay out a method for solving the Volterra equation $\solwhole = \volterra \solwhole$ from Section~\ref{setting}. Recall that $\volterra$ is the sum of a separable operator $\hardpart$, which has a regular singularity at $\zeta = 0$, and a perturbation $\softpart$.

\color{SeaGreen}
In this section, we'll prove the results stated in Section~\ref{sec:results}. Our arguments will follow the process of solving the regular singular Volterra equation $\solwhole = \volterra \solwhole$ by Picard iteration.

The prototype solution $\solproto$ is our initial guess. When we apply $\volterra = \hardpart + \softpart$ to it, the singular part $\hardpart$ leaves it unchanged, as we'll show in Section~\ref{sec:construction}. In addition, $\solproto$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$, as shown in Section~\ref{sec:asymptotics}.\textcolor{RoyalBlue}{We'll show in Section~\ref{sec:asymptotics} that $\solproto$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$.}

To see what the perturbation $\softpart$ does to $\solproto$, we'll show in Section~\ref{sec:image under soft_part} that $\softpart$ has a smoothing effect, reducing the sharpness of any power-law singularity at $\zeta = 0$. In particular, it sends $\solproto$ into $\singexpalg{\tau-1+\epsilon}(\domain)$. The perturbed operator $\volterra$ therefore sends $\solproto$ into the affine subspace $\solproto + \singexpalg{\tau-1+\epsilon}(\domain)$.

When we apply $\volterra$ again, it contracts the perturbation term $\solptb$ in $\singexpalg{\tau-1+\epsilon}(\domain)$. More precisely, by making $\Lambda$ large enough, we can ensure that the subspace $\singexp{\tau+1+\epsilon}{\Lambda}(\domain)$ both contains the perturbation term and is contracted by $\volterra$. We'll prove this in Section~\ref{sec:V is a contraction}.

\color{RoyalBlue}
We can now see that at each stage of the Picard iteration process, we start with an approximate solution of the form
\[ \solproto + \solptb, \]
with $\solptb \in \singexp{\tau-1+\epsilon}{\Lambda}(\domain)$. Applying $\volterra$ gives 
\[ \solproto + \softpart \solproto + \volterra \solptb, \]
where the perturbation $\solptb$ has been contracted by $\volterra$, and $\softpart f_0$ has been smoothed and it lies in the same function space as $\solptb$. The contraction mapping theorem guarantees the existence and uniqueness of the fixed point 
\[ \solptb = \softpart \solproto + \volterra \solptb. \]
We'll fill out the details of this argument in Section~\ref{sec:existence and uniqueness}.

\color{MediumBlue}
We can now see that at each stage of the Picard iteration process, we have an approximate solution of the form
\[ \solproto + \solptb, \]
with $\solptb \in \singexp{\tau-1+\epsilon}{\Lambda}(\domain)$. Applying $\volterra$ gives us the new approximate solution
\[ \solproto + \softpart \solproto + \volterra \solptb, \]
where the perturbation $\solptb$ has been contracted by $\volterra$ but also augmented with another $\softpart \solproto$. The contraction mapping theorem guarantees that these opposing processes will eventually balance out, bringing us to a unique fixed point where
\[ \solptb = \softpart \solproto + \volterra \solptb. \]
We'll fill out the details of this argument in Section~\ref{sec:existence and uniqueness}.
\color{black}
%%To prove that the Picard iteration process converges, we'll show in Section~\ref{sec:V is a contraction} that $\volterra$ shrinks perturbations

%%To see what the perturbation $\softpart$ does to $\solproto$, we first show in Section~\ref{sec:asymptotics} that $\solproto$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\Omega)$. We then show in Section~\ref{sec:image under soft_part} that $\softpart$ has the

%%The results stated in Section~\ref{sec:results} lay out a method for solving the regular singular Volterra equation $\solwhole = \volterra \solwhole$. In this section, we prove the results, showing that our solution method works as expected.

%%In this section, we'll prove the results stated in Section~\ref{sec:results}, which lay out a method for solving the regular singular Volterra equation $\solwhole = \volterra \solwhole$ from Section~\ref{setting}. We start by constructing the {\em prototype solution} $\solproto$ of the simpler equation $\solwhole = \hardpart \solwhole$, which has essentially the same singularity.

%%The plan starts with the explicit

%%The first step of the plan is to construct the {\em prototype solution} $\solproto$, which satisfies the simpler equation $\solwhole = \hardpart \solwhole$. In Section~\ref{sec:proto-construction-regularity}, we

%%with the ultimate goal of proving Theorem~\ref{thm:general_volterra}. This theorem says that we can solve the regular singular Volterra equation $\solwhole = \volterra \solwhole$ by first constructing the {\em prototype solution} $\solproto$, which explicitly describes what's going on near the singularity, and then adding a less singular perturbation $\solptb$.

%%the explicit {\em prototype solution} $\solproto$ of the prototypical regular singular Volterra equation $\solwhole = \hardpart \solwhole$ can be perturbed uniquely

%%when we perturb the prototypical regular singular Volterra equation $\solwhole = \hardpart \solwhole$ to the more general equation $\solwhole = \volterra \solwhole$, the prototype solution $\solproto$ gets perturbed

%%the equation $\solwhole = \volterra \solwhole$ has a unique solution of the form $\solproto + \solptb$, where the {\em prototype solution} $\solproto$ captures

%%This equation says that once we have the {\em prototype solution} $\solproto$ of the prototypical regular singular Volterra equation $\solwhole = \hardpart \solwhole$, we can

%%This theorem says that if we start with a certain explicit solution $\solproto$ of the equation $\solwhole = \hardpart \solwhole$,

%%This theorem says that we can solve the regular singular Volterra equation $\solwhole = \volterra \solwhole$ by splitting $\volterra$ into the singular part $\hardpart$ and the perturbation $\softpart$,

%%constructing an explicit {\em prototype solution} of the equation $\solwhole = \hardpart \solwhole$

%%This theorem says that for a perturbed Volterra operator $\volterra = \hardpart + \softpart$ of the kind described in Section~\ref{setting}, the equation $\solwhole = \volterra \solwhole$ has a unique solution of the form $\solproto + \solptb$, where $\solproto = \hardpart \solproto$ and $\solptb$ is a less singular perturbation.
\begin{brainstorm}
\item Explain how we're going to prove Theorem~\ref{thm:general_volterra}.
\item Roughly follow the sections. Eventual goal: make section titles match proof steps.
\begin{itemize}
\item Link to subsections during description.
\end{itemize}
\item Rough sketch of proof story:
\begin{itemize}
    \item Construct prototype solution $f_0$. Show it's in $\singexp{\tau-1}{\lambda_0}$.
    \item Show that $\softpart$ maps $f_0$ into $\singexp{\tau-1+\varepsilon}{\Lambda}$ for $\Lambda\geq\lambda_\Delta$ (see Corollary \ref{cor:pertub_f0}).
    \item Show that $\volterra$ contracts $\singexp{\rho-1}{\Lambda}$ when $\rho > \tau$ and $\Lambda$ is big enough (done in Proposition \ref{prop:get-contraction}).
    \item Use the contraction mapping theorem to prove Lemma~\ref{lem:perturbed_volterra}, and then use that lemma to prove Theorem~\ref{thm:general_volterra}.
\end{itemize}
\end{brainstorm}
\subsection{Bounds on the perturbed kernel}\label{sec:bounds on k}
\subsubsection{Overview}
The conditions on $\hardker$ and $\softker$ described in Sections \ref{setting:basic} and \ref{setting:perturbed} can be combined into convenient bounds on the kernel $\kerwhole = \hardker + \softker$ of $\volterra$. We'll use these bounds in Section~\ref{sec:V is a contraction}. \textcolor{orange}{[Are these bounds actually used in Section~\ref{sec:existence and uniqueness}, or anywhere else? If not, maybe we should move this stuff into Section~\ref{sec:V is a contraction} after all.]}
\subsubsection{Bounds near the origin}
When $\hardpart$ satisfies Condition~\eqref{cond:sing} and $\softpart$ satisfies Condition~\eqref{cond:eps-lambda}, we can estimate the kernel $\kerwhole$ near $\zeta=0$.

@@

\[
\frac{1}{|p'(\alpha)+b_2(\zeta(a)-\alpha)+b_3(\zeta(a)-\alpha)^2+...|}\leq 
\]

>>>>

Now we know that $\volterra$ sends $\solproto$ into the affine subspace $\solproto + \singexpalg{\tau-1+\epsilon}(\domain)$, suggesting that the equation $\solwhole = \volterra \solwhole$ has a solution there. To confirm this, we'll show in Section~\ref{sec:V is a contraction} that $\volterra$ is a contraction of $\singexp{\tau-1+\epsilon}{\Lambda}(\domain)$ when $\Lambda$ is large enough. This tells us that $\volterra$ has a unique fixed point in $\solproto + \singexpalg{\tau-1+\epsilon}(\domain)$, as we'll see in Section~\ref{sec:existence and uniqueness}.
\subsection{Bounds on the perturbed kernel}\label{sec:bounds on k}
\subsubsection{Overview}
The conditions on $\hardker$ and $\softker$ described in Sections \ref{setting:basic} and \ref{setting:perturbed} can be combined into convenient bounds on the kernel $\kerwhole = \hardker + \softker$ of $\volterra$. We'll use these bounds in Section~\ref{sec:V is a contraction}. \textcolor{orange}{[Are these bounds actually used in Section~\ref{sec:existence and uniqueness}, or anywhere else? If not, maybe we should move this stuff into Section~\ref{sec:V is a contraction} after all.]}
\subsubsection{Bounds near the origin}
When $\hardpart$ satisfies Condition~\eqref{cond:sing} and $\softpart$ satisfies Condition~\eqref{cond:eps-lambda}, we can estimate the kernel $\kerwhole$ near $\zeta=0$.

@@

\[
\frac{1}{|p'(\alpha)+b_2(\zeta(a)-\alpha)+b_3(\zeta(a)-\alpha)^2+...|}\leq  \text{const.}  
\]
